Follow-up Samples

### 2017-01-09 submission/manuscript_outline_20161024.Rmd

**Figure 3: Graph of the Receiver Operating Characteristic Curve on Test Set Performance of the Best, Middle, Worse, and Full Training Models.** For each of the 100 training cohort sets used had `r round(length(rownames(metaI))*0.8)` individuals and the testing cohort sets had `r round(length(rownames(good_metaf))*0.2)` individuals.  The AUC on the test sets for the best, middle, and worse models from training were `r format(model_test_AUC_summary["best", "AUC"], digits = 3)`, `r format(model_test_AUC_summary["middle", "AUC"], digits = 3)`, and `r format(model_test_AUC_summary["worse", "AUC"], digits = 3)`, respectively.  cvAUC is the 20 times repeated 10-fold cross-validated AUC from training.

>>>>

**Figure 3: Graph of the Receiver Operating Characteristic Curve for lesion and Initial/Follow up models.** The shaded areas represents the range of values of a 100 different 80/20 splits of the test set data using either all variables (grey) or reduced variable (red) models.  The blue line represents the reduced variable model using 100% of the data set.  A) Lesion model.  B) Initial/Follow up model

### 2017-01-09 submission/manuscript_outline_20161024.tex

In our training set we show that the overall community structure as
measured by different alpha diversity metrics, shows very little change
between controls and those with either adenoma or carcinoma {[}Table
S1{]}. With respect to our test set there was very little difference in
magnitude of change in the thetayc distance metric between those with
adenoma or carcinoma {[}Figure 1a{]}. In contrast, FIT had a large
change in the initial and follow up samples in the carcinoma group
versus the adenoma {[}Figure 1b{]}. An NMDS showed that there was very
little observable change between initial and follow up for the adenoma
group but there was one for the carcinoma group {[}Figure 2{]}. This
cursory information is suggestive that treatment of carcinoma, had the
largest response.

@@

\textbf{Figure 1: Change in Thetayc and Fit between initial and follow
up in adenoma or carcinoma group.} A) No significant difference was
found between the adenoma and carcinoma group for thetayc (P-value =
0.00198). B) A significant difference was found between the adenoma and
carcinoma group for FIT (P-value = 2.15e-05).

\textbf{Figure 2: NMDS of the Overall Bacterial Community Changes.} A)
NMDS of the intial and follow up samples for the Adenoma group. B) NMDS
of the initial and follow up samples for the Carcinoma group.

\textbf{Figure 3: Graph of the Receiver Operating Characteristic Curve
on Test Set Performance of the Best, Middle, Worse, and Full Training
Models.} For each of the 100 training cohort sets used had 392
individuals and the testing cohort sets had 13 individuals. The AUC on
the test sets for the best, middle, and worse models from training were
0.646, 0.744, and 0.904, respectively. cvAUC is the 20 times repeated
10-fold cross-validated AUC from training.

@@

\textbf{Figure 6: Previously Associated CRC Bacteria in Initial and
Follow up Samples.} A) Carcinoma initial and follow up samples. There
was a significant difference in initial and follow up sample for the
OTUs classfied as Peptostreptococcus stomatis (P-value = 0.0183) and
Porphyromonas asaccharolytica (P-value = 0.0154). B) Adenoma initial and
follow up samples. There were no significant differences between initial
and follow up.

>>>>

In our training set we show that the overall community structure as
measured by different alpha diversity metrics, shows very little change
between controls and those with either adenoma or carcinoma {[}Table
S1{]}. With respect to our test set there was very little difference in
magnitude of change in the thetayc distance metric between those with
adenoma or carcinoma {[}Figure 1a{]}. In contrast, FIT had a large
change in the initial and follow up samples in the carcinoma group
versus the adenoma {[}Figure 1b{]}. An NMDS showed that there was very
little observable change between initial and follow up for the adenoma
group but there was one for the carcinoma group {[}Figure 1c \& 1d{]}.
This cursory information is suggestive that treatment of carcinoma, had
the largest response.

@@

\textbf{Figure 1: Changes and differences between the adenoma or
carcinoma group.} A) No significant difference was found between the
adenoma and carcinoma group for thetayc (P-value = 0.00198). B) A
significant difference was found between the adenoma and carcinoma group
for FIT (P-value = 2.15e-05). C) NMDS of the intial and follow up
samples for the Adenoma group. D) NMDS of the initial and follow up
samples for the Carcinoma group. For C) and D) the teal represents
initial samples and the pink represents follow up samples.

\textbf{Figure 2: Previously Associated CRC Bacteria in Initial and
Follow up Samples.} A) Carcinoma initial and follow up samples. There
was a significant difference in initial and follow up sample for the
OTUs classfied as Peptostreptococcus stomatis (P-value = 0.0183) and
Porphyromonas asaccharolytica (P-value = 0.0154). B) Adenoma initial and
follow up samples. There were no significant differences between initial
and follow up.

\textbf{Figure 3: Graph of the Receiver Operating Characteristic Curve
for lesion and Initial/Follow up models.} The shaded areas represents
the range of values of a 100 different 80/20 splits of the test set data
using either all variables (grey) or reduced variable (red) models. The
blue line represents the reduced variable model using 100\% of the data
set. A) Lesion model. B) Initial/Follow up model

@@
